\vspace{-3em} \LARGE Hamiltonian Privilege

### 2023-03-06 Articles/2020-ClassicalMechanicsPhil/Submissions/ERKE/classical-phil-article-Erkenntnis.tex
ClassMechPhil: minor change

\noindent
This assumption characterizes classical systems as those whose infinitesimal parts completely specify the state of the system. We define a \textit{classical particle} as one of these infinitesimal parts, namely the limit of recursive subdivision.\footnote{This definition of a classical particle differs from viewing point-particles as extensionless \parencites[]{Butterfieldpoints} or zero-dimensional \parencites[]{Wilson}.} {\color{green} Ultimately, this condition entails that we can describe the state of the whole system as a statistical distribution over the state space of its parts. If we model the state space of the parts using a manifold, this manifold must be differentiable so that it can support a density at each point. Moreover, given that this density must be a function of the state, and not of the coordinates, we show that the manifold must be symplectic.}
% % Could add: readers who are satisfied with this overview can proceed to the next subsection
% % % For further discussion, see \textcites{shpmp}. [omit this for review].

>>>>

\noindent
This assumption characterizes classical systems as those whose infinitesimal parts completely specify the state of the system. We define a \textit{classical particle} as one of these infinitesimal parts, namely the limit of recursive subdivision.\footnote{This definition of a classical particle differs from viewing point-particles as extensionless \parencites[]{Butterfieldpoints} or zero-dimensional \parencites[]{Wilson}.} {\color{green} Ultimately, this condition entails that we can describe the state of the whole system as a statistical distribution over the state space of its parts. If we model the state space of the parts using a manifold, the distribution must be characterized by a density that depends on the state, and not on the coordinates, which leads us to find that the manifold must be symplectic.}
% % Could add: readers who are satisfied with this overview can proceed to the next subsection
% % % For further discussion, see \textcites{shpmp}. [omit this for review].
